Inferring the distribution and rate of Earth-like exoplanets \\ from noisy individual-planet inferences

### 2014-03-25 document/ms.tex
petigura

\newcommand{\nyu}{2}
\newcommand{\mpia}{3}
\newcommand{\princeton}{4}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    David~W.~Hogg\altaffilmark{\nyu,\mpia},
    Timothy~D.~Morton\altaffilmark{\princeton},
    \etal
}
\altaffiltext{1}            {To whom correspondence should be addressed:
                             \url{danfm@nyu.edu}}
\altaffiltext{\nyu}         {Center for Cosmology and Particle Physics,
                             Department of Physics, New York University,
                             4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\mpia}        {Max-Planck-Institut f\"ur Astronomie,
                             K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\princeton}   {Department of Astrophysics, Princeton University,
                             Princeton, NJ, 08540, USA} % CHECK THIS ZIP CODE

>>>>

\newcommand{\nyu}{2}
\newcommand{\mpia}{3}
\newcommand{\princeton}{4}
\author{%
    Daniel~Foreman-Mackey\altaffilmark{1,\nyu},
    David~W.~Hogg\altaffilmark{\nyu,\mpia},
    Timothy~D.~Morton\altaffilmark{\princeton},
    Erik~Petigura\altaffilmark{\berkeley},
    \etal
}
\altaffiltext{1}         {To whom correspondence should be addressed:
                          \url{danfm@nyu.edu}}
\altaffiltext{\nyu}      {Center for Cosmology and Particle Physics,
                          Department of Physics, New York University,
                          4 Washington Place, New York, NY, 10003, USA}
\altaffiltext{\mpia}     {Max-Planck-Institut f\"ur Astronomie,
                          K\"onigstuhl 17, D-69117 Heidelberg, Germany}
\altaffiltext{\princeton}{Department of Astrophysics, Princeton University,
                          Princeton, NJ, 08540, USA} % CHECK THIS ZIP CODE
\altaffiltext{\berkeley} {Department of Astronomy, University of California at Berkeley,
                          Berkeley, CA, XXXXX, USA} % CHECK THIS ZIP CODE
